Derogations and emergency policies

### 2023-04-20 analysis/analysis_policies.qmd
Rename; go to 5946ab5 for previous history
Going to 5946ab5 and seeing the history of /analysis/analysis_prelim.qmd and /analysis/analysis_h1.qmd will show the whole past history

```{r}
prelim_trace <- function(model) {
  model %>% 
    gather_draws(b_Intercept, b_derogation_ineffect, b_year_week_num, sd_country_name__Intercept) %>% 
    ggplot(aes(x = .iteration, y = .value, color = factor(.chain))) +
    geom_line(linewidth = 0.1) +
    scale_color_viridis_d(option = "rocket", end = 0.85) +
    labs(color = "Chain") +
    facet_wrap(vars(.variable), scales = "free_y") +
    theme_pandem()
}

prelim_trank <- function(model) {
  model %>% 
    gather_draws(b_Intercept, b_derogation_ineffect, b_year_week_num, sd_country_name__Intercept) %>% 
    group_by(.variable) %>% 
    mutate(draw_rank = rank(.value)) %>% 
    ggplot(aes(x = draw_rank, color = factor(.chain))) +
    stat_bin(geom = "step", binwidth = 200, position = position_identity(), boundary = 0) +
    scale_color_viridis_d(option = "rocket", end = 0.85) +
    labs(color = "Chain") +
    facet_wrap(vars(.variable), scales = "free_y") +
    theme_pandem()
}

prelim_pp <- function(model) {
  pp_check(model, ndraws = 100, type = "bars")
}
```

@@

```{r}
prelim_trace(m_prelim_derog$model[[1]])
```

```{r}
prelim_trank(m_prelim_derog$model[[1]])
```

```{r}
prelim_pp(m_prelim_derog$model[[1]])
```

@@

```{r}
prelim_trace(m_prelim_derog$model[[2]])
```

```{r}
prelim_trank(m_prelim_derog$model[[2]])
```

```{r}
prelim_pp(m_prelim_derog$model[[2]])
```

@@

```{r}
prelim_trace(m_prelim_derog$model[[3]])
```

```{r}
prelim_trank(m_prelim_derog$model[[3]])
```

```{r}
prelim_pp(m_prelim_derog$model[[3]])
```

@@

```{r}
prelim_trace(m_prelim_derog$model[[4]])
```

```{r}
prelim_trank(m_prelim_derog$model[[4]])
```

```{r}
prelim_pp(m_prelim_derog$model[[4]])
```

@@

```{r}
prelim_trace(m_prelim_derog$model[[5]])
```

```{r}
prelim_trank(m_prelim_derog$model[[5]])
```

```{r}
prelim_pp(m_prelim_derog$model[[5]])
```

>>>>

```{r}
params_to_show <- c("b_Intercept", "b_derogation_ineffect", 
                    "b_year_week_num", "sd_country_name__Intercept")
```

@@

```{r}
plot_trace(m_prelim_derog$model[[1]], params_to_show)
```

```{r}
plot_trank(m_prelim_derog$model[[1]], params_to_show)
```

```{r}
plot_pp(m_prelim_derog$model[[1]])
```

@@

```{r}
plot_trace(m_prelim_derog$model[[2]], params_to_show)
```

```{r}
plot_trank(m_prelim_derog$model[[2]], params_to_show)
```

```{r}
plot_pp(m_prelim_derog$model[[2]])
```

@@

```{r}
plot_trace(m_prelim_derog$model[[3]], params_to_show)
```

```{r}
plot_trank(m_prelim_derog$model[[3]], params_to_show)
```

```{r}
plot_pp(m_prelim_derog$model[[3]])
```

@@

```{r}
plot_trace(m_prelim_derog$model[[4]], params_to_show)
```

```{r}
plot_trank(m_prelim_derog$model[[4]], params_to_show)
```

```{r}
plot_pp(m_prelim_derog$model[[4]])
```

@@

```{r}
plot_trace(m_prelim_derog$model[[5]], params_to_show)
```

```{r}
plot_trank(m_prelim_derog$model[[5]], params_to_show)
```

```{r}
plot_pp(m_prelim_derog$model[[5]])
```
